### 2021-10-24 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_bumblebees@81f4d8850cb6ac9d31f9412fdc64c14e79a3b03c 🚀
Deploying to gh-pages from @ gottacatchenall/ms_bumblebees@3e3fe34c3ae3b650fbde211b7860deca8b36e095 🚀

%
\href{https://orcid.org/0000-0002-6506-6487}{Michael D.\,Catchen}%
%
\,\textsuperscript{1,2}\quad %
\href{https://orcid.org/0000-0001-9051-0597}{Francis\,Banville}%
%
\,\textsuperscript{3,4,2}\quad %
Paul\,CaraDonna%
%
\,\textsuperscript{5,6,‡}\quad %
\href{https://orcid.org/0000-0002-2151-6693}{Dominique\,Caron}%
%
\,\textsuperscript{1,2}\quad %
\href{https://orcid.org/0000-0002-6248-3007}{Philippe\,Desjardins-Proulx}%
%
\,\textsuperscript{3,2}\quad %
\href{https://orcid.org/0000-0001-9019-0108}{Norma R.\,Forero-Muñoz}%
%
\,\textsuperscript{3,2}\quad %
\href{https://orcid.org/0000-0001-6075-8081}{Andrew\,Gonzalez}%
%
\,\textsuperscript{1,2}\quad %
\href{https://orcid.org/0000-0002-4498-7076}{Dominique\,Gravel}%
%
\,\textsuperscript{4,2}\quad %
Jane E.\,Ogilvie%
%
\,\textsuperscript{5,‡}\quad %
\href{https://orcid.org/0000-0002-6004-4027}{Laura\,Pollock}%
%
\,\textsuperscript{1,2}\quad %
\href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
%
\,\textsuperscript{3,2,‡}\quad %
\href{https://orcid.org/0000-0001-6067-1349}{Tanya\,Strydom}%
%
\,\textsuperscript{3,2,‡}\quad %
Julian\,Resasco%
%
\,\textsuperscript{7,‡}

@@

\textsuperscript{‡}\,These authors contributed equally to the work\\

@@

\begin{itemize}
\tightlist
\item
  dispersal capacity and range shifts
\end{itemize}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\setcounter{enumi}{1}
\tightlist
\item
  Phenological uncoupling {[}cite{]}.
\end{enumerate}

@@

@@

\hypertarget{models}{%
\subsection{Models}\label{models}}

>>>>

%
\href{https://orcid.org/0000-0002-6506-6487}{Michael D.\,Catchen}%
%
\,\textsuperscript{1,2}\quad %
\href{https://orcid.org/0000-0001-9051-0597}{Francis\,Banville}%
%
\,\textsuperscript{3,4,2}\quad %
Paul\,CaraDonna%
%
\,\textsuperscript{5,6}\quad %
\href{https://orcid.org/0000-0002-2151-6693}{Dominique\,Caron}%
%
\,\textsuperscript{1,2}\quad %
\href{https://orcid.org/0000-0002-6248-3007}{Philippe\,Desjardins-Proulx}%
%
\,\textsuperscript{3,2}\quad %
\href{https://orcid.org/0000-0001-9019-0108}{Norma R.\,Forero-Muñoz}%
%
\,\textsuperscript{3,2}\quad %
\href{https://orcid.org/0000-0001-6075-8081}{Andrew\,Gonzalez}%
%
\,\textsuperscript{1,2}\quad %
\href{https://orcid.org/0000-0002-4498-7076}{Dominique\,Gravel}%
%
\,\textsuperscript{4,2}\quad %
Jane E.\,Ogilvie%
%
\,\textsuperscript{5}\quad %
\href{https://orcid.org/0000-0002-6004-4027}{Laura\,Pollock}%
%
\,\textsuperscript{1,2}\quad %
\href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
%
\,\textsuperscript{3,2}\quad %
\href{https://orcid.org/0000-0001-6067-1349}{Tanya\,Strydom}%
%
\,\textsuperscript{3,2}\quad %
Julian\,Resasco%
%
\,\textsuperscript{7}

@@

@@

\begin{itemize}
\tightlist
\item
  range shifts in latitude context
\item
  apply this to elevational gradients
\item
  dispersal capacity and range shifts
\end{itemize}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\setcounter{enumi}{1}
\tightlist
\item
  Phenological uncoupling (\textbf{Olesen2011MisFor?}).
\end{enumerate}

@@

In this paper we\ldots. combine data from a variety of sources: field
data from several sites, crowd-sourced data (GBIF), and remotely-sensed
data. to produce a \emph{spatially and temporally explict} metaweb of
bumblebee-flower interactions across Colorado. We then estimate the
change in spatial and temporal overlap over time using the CMIP6 climate
consensus forecast (\textbf{Karger2017CliHig?}).

@@

This project involves assembly and integration of data from a variety of
(both structured and unstructured) sources. This data can be divided
into four categories: field data, GBIF data, remote-sensing data, and
phylogenetic data.

\hypertarget{field-data}{%
\subsubsection{Field data}\label{field-data}}

The field data consists of: (1) a seven year data-set from Rocky
Mountain Biological Laboratory, consisting of season-long interaction
and phenology data six plots along an elevation gradient. (2) a similar
six year data set from Elk Meadows, CO, and (3) a year across a large
elevation gradient at Pikes Peak.

Additional in-situ environmental sensors.

The partitioning of this data into training, test, and validation sets
if described in the \emph{Models} section.

\hypertarget{gbif-data}{%
\subsubsection{GBIF data}\label{gbif-data}}

The data from Global Biodiversity Information Facility (GBIF) itself
comes in two forms: (1) spatial records of bumblebee and flower records
(2) sparsely available records of the plants a bee was observed on (TODO
details from Julian).

\hypertarget{remote-sensing-data}{%
\subsubsection{Remote-sensing data}\label{remote-sensing-data}}

The remote-sensing data consists of high-resolution LiDAR elevation data
at 1 meter spatial resolution
{[}(\textbf{NationalEcologicalObservatoryNetworkNEON2021EleLid?});{]},
and daily 1km resolution precipitation and temperature from CHELSA
(\textbf{Karger2021GloDai?}).

\hypertarget{phylogenic-data}{%
\subsubsection{Phylogenic data}\label{phylogenic-data}}

The phylogenetic data consists of genomic barcodes available from NCBI
GenBank.

\hypertarget{a-spatiotemporally-explicit-predictive-metaweb-model}{%
\subsection{A spatiotemporally explicit predictive metaweb
model}\label{a-spatiotemporally-explicit-predictive-metaweb-model}}

What does it mean for it to be ``spatiotemporally explicit?'' Well the
formal definition of a metaweb is total species pool and
